\myTitle

### 2024-05-07 body-text-of-paper.tex
made some edits

A best practice for evaluating the behavior of genetic clustering algorithms on empirical data is to conduct
parallel analyses on simulated data that mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine} while providing
the benefit of known parameters (e.g.~$F_\mathrm{ST}$, admixture fractions, etc.) that can
be compared to estimates.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see, for example, \citealt{nielsen2006hybridlab,kinziger2008hybridization}).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals (or segments of the genome) back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations $[BC_1, \ldots,
BC_X])$.
Evaluating the results and resolution of genetic clustering algorithms in the context of data that are
expected to arrive by such a process of hybridization requires simulation of
explicit hybrids.  Such simulations are the purpose of the software {\sc hybridlab} 
\citep{nielsen2006hybridlab}.

@@

To construct this simple example, we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.

>>>>

A best practice for evaluating the behavior of genetic clustering algorithms on empirical data is to conduct
parallel analyses on simulated data that mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine} while providing
the benefit of known parameters (e.g.~$F_\mathrm{ST}$, admixture fractions, etc.) that can
be compared to estimates.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see, for example, \citealt{nielsen2006hybridlab,kinziger2008hybridization}).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals (or segments of the genome) back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations $[BC_1, \ldots,
BC_X])$.
Evaluating the results and resolution of genetic clustering algorithms in the context of data that are
expected to reflect a history of hybridization requires simulation of
explicit hybrids.  Such simulations are the purpose of the software {\sc hybridlab} 
\citep{nielsen2006hybridlab}.

@@

To construct this simple illustration of sampling-with-replacement induced RISPI, 
we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.
